---
title: "CLT"
author: "Saul Perez Ramos"
date: '2022-06-08'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
Originalmean<-mean(my1000)
OriginalSD<-sd(my1000)
options(digits=1)
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 
The mean on the original data is `r Originalmean`  standard deviation is `r OriginalSD`.



Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
sample2mean<-mean(x.avg)
sample2sd<-sd(x.avg)
```

The plot is not unimodal.There are also three peaks for a sample size of two. The two peaks on opposite ends are the same size but the one in the middle is far greater. the average mean is `r sample2mean` and standard deviation is `r sample2sd`

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
sample4mean<-mean(x.avg)
sample4sd<-sd(x.avg)
```

The mean for sample 4 is `r sample4mean` and standard deviation for sample 4 is `r sample4sd`
There 5 peaks in sample size 4 with them being 4 people not liking her to 1 out 4, then to 2 out of 4 liking her, 3 out of 4 liking her and lastly 4 out of 4 liking her. With the highest peak being at 2 out of 4 people liking her. 

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
sample9mean<-mean(x.avg)
sample9sd<-sd(x.avg)
```

Sample 9 mean is `r sample9mean` and Sample 9 standard deviation is `r sample9sd`

```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
sample16mean<-mean(x.avg)
sample16sd<-sd(x.avg)
```

Sample 16 mean is `r sample16mean` and Sample 16 standard deviation is `r sample16sd`

```{r}
numb = 25
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 25")
sample25mean<-mean(x.avg)
sample25sd<-sd(x.avg)
```

Sample 25 mean is `r sample25mean` and Sample 25 standard deviation is `r sample25sd`

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
sample36mean<-mean(x.avg)
sample36sd<-sd(x.avg)
```

Sample 36 mean is `r sample36mean` and Sample 36 standard deviation is `r sample36sd`